### 2022-05-24 paper.Rmd
implemented new example 1 (including skew now) in paper

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

path <- "results_oasis_same_size.csv"

@@

  K <- 9
  mean_sd_tabs <- list()
  for (criterion in c("kplus", "variance", "diversity")) {
    oasis[[paste(criterion, "group", sep = "_")]] <- anticlustering(
      features,
      standardize = TRUE,
      K = K,
      objective = criterion,
      method = "local-maximum"
    )
    mean_sd_tabs[[criterion]] <- mean_sd_tab(
      features,
      oasis[[paste(criterion, "group", sep = "_")]]
    )
    mean_sd_tabs[[criterion]] <- cbind(
      1:K,
      nrow(features) / K,
      mean_sd_tabs[[criterion]]
    )
  }

apa_table(
  oasis_tab,
  caption = "Descriptive statistics for OASIS features by group and anticlustering method.",
  note = "The cells contain mean values by cluster and the standard deviation (in parentheses).",
  escape = FALSE,
  align = c("r"),
  stub_indents = list("\\textbf{K-plus anticlustering}" = 1:9,
                      "\\textbf{K-means anticlustering}" = 10:18,
                      "\\textbf{Anticluster editing}" = 19:27)
)
```

>>>>

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
# for formatting numbers in Rmarkdown, use my package prmisc (https://github.com/m-Py/prmisc)
library("prmisc") # remotes::install_github("m-Py/prmisc") 
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

example1_file <- "results_oasis_same_size.csv"
if (!file.exists(example1_file)) {

    oasis <- read.csv(
    "https://raw.githubusercontent.com/aenneb/OASIS-beauty/master/means_per_image.csv"
    )

@@

    K <- 9

    # k-plus variance / skew
    groups_kplus <- kplus_anticlustering(
        features,
        K = K,
        variance = TRUE,
        skew = TRUE,
        method = "local-maximum",
        standardize = TRUE
    )

    # k-means
    groups_kmeans <- anticlustering(
        features,
        K = K,
        objective = "variance",
        method = "local-maximum",
        standardize = TRUE
    )

    # diversity
    groups_diversity <- anticlustering(
        features,
        K = K,
        objective = "diversity",
        method = "local-maximum",
        standardize = TRUE
    )

    # Functions to compute means / SD / skew per group 
    descriptives_by_group <- function(features, anticlusters, FUN, name) {
        df <- data.frame(
            t(data.frame(lapply(by(features, anticlusters, FUN), c)))
        )
        df$group <- 1:nrow(df)
        df$Descriptive = name
        df
    }

    all_descriptives_by_group <- function(features, anticlusters) {
    means <- descriptives_by_group(features, anticlusters, colMeans, "mean")
    sds <- descriptives_by_group(
        features, 
        anticlusters, 
        function(x) sapply(x, sd),
        "sds"
    )
    skew <- descriptives_by_group(
        features, 
        anticlusters, 
        function(x) sapply(x, DescTools::Skew),
        "skew"
    )
    rbind(means, sds, skew)
    }

    kplus <- all_descriptives_by_group(features, groups_kplus)
    kplus <- data.frame(kplus, Objective = "kplus")

    kmeans <- all_descriptives_by_group(features, groups_kmeans)
    kmeans <- data.frame(kmeans, Objective = "kmeans")
    diversity <- all_descriptives_by_group(features, groups_diversity)
    diversity <- data.frame(diversity, Objective = "diversity")

    all_objs <- rbind(kplus, kmeans, diversity) %>% 
    pivot_wider(names_from = Descriptive, values_from = c(beauty_mean, Valence_mean, Arousal_mean))

    write.table(
        all_objs, example1_file, row.names = FALSE, sep = ";"
    )

} else {
  all_objs <- read.csv(example1_file, sep = ";")
}

table_all_objs <- subset(all_objs, select = -Objective)
table_all_objs <- as.matrix(table_all_objs)
colnames(table_all_objs) <- c("Group", rep(c("$M$", "$\\mathit{SD}$", "Skew"), 3))
table_all_objs <- apply(table_all_objs, 2, force_or_cut)
#mode(table_all_objs) <- "character"

apa_table(
  table_all_objs,
  caption = "Descriptive statistics for OASIS features by group and anticlustering method.",
  note = "The k-plus approach minimized differences with regard to means, variances and skew.",
  escape = FALSE,
  align = c("c", rep("r", 9)),
  col_spanners = list(Beauty = c(2, 4), Valence = c(5, 7), Arousal = c(8, 10)), 
  stub_indents = list("\\textbf{K-plus anticlustering}" = 1:9,
                      "\\textbf{K-means anticlustering}" = 10:18,
                      "\\textbf{Diversity anticlustering}" = 19:27)
)
```
